---
title: "Red Wines Exploration"
author: "Sara Uenoyama"
date: "December 12, 2018"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

This report explores a dataset containing quality and attributes 
for approximately 1600 bottles of red wine.

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
### Packages
# Load all of the packages that you end up using in your analysis in this code
# chunk.

r = getOption("repos")
r["CRAN"] = "http://cran.stat.nus.edu.sg/"
options(repos = r)

install.packages("ggplot2")
install.packages("knitr")
install.packages("dplyr")
install.packages("PerformanceAnalytics")
install.packages("memisc")
install.packages("wesanderson")
install.packages("ggforce")

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

```


```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(ggplot2)
library(knitr)
library(dplyr)
library(gridExtra)
library(PerformanceAnalytics)
library(memisc)
library(wesanderson)
library(ggforce)
library(units)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
### global setting
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)

```

```{r echo=FALSE, Load_the_Data, message=FALSE, warning=FALSE}
# Load the Data
wineQualityReds <- read.csv('wineQualityReds.csv')
```


# Univariate Plots Section

The numbers of rows and columns in the data are

```{r echo=FALSE, Univariate_Plots}
# this project ...
nrow(wineQualityReds)
ncol(wineQualityReds)
```

```{r}
# create quality as factor data 
wineQualityReds$quality.factor <- as.factor(wineQualityReds$quality)
```

  

```{r}
str(wineQualityReds)
```

```{r}
summary(wineQualityReds)
```

Our dataset consists of 13 variables, with almost 1,600 observations.

```{r}
ggplot(wineQualityReds, aes(x=factor(quality))) + geom_bar()

```

Mostly red wine quality is 5 or 6. Why most of the wine quality falls into 5 or 
6? What makes wine of better quality? Are those too poory or highly evaluated 
wines outliers? I wonder what this plot looks like across other variables.  

```{r}
qplot(data = wineQualityReds, x = fixed.acidity)
summary(wineQualityReds$fixed.acidity)

qplot(data = wineQualityReds, x = volatile.acidity)
summary(wineQualityReds$volatile.acidity)

qplot(data = wineQualityReds, x = citric.acid)
summary(wineQualityReds$citric.acid)

qplot(data = wineQualityReds, x = residual.sugar)
summary(wineQualityReds$residual.sugar)

qplot(data = wineQualityReds, x = chlorides)
summary(wineQualityReds$chlorides)

qplot(data = wineQualityReds, x = free.sulfur.dioxide)
summary(wineQualityReds$free.sulfur.dioxide)

qplot(data = wineQualityReds, x = total.sulfur.dioxide)
summary(wineQualityReds$total.sulfur.dioxide)

qplot(data = wineQualityReds, x = density)
summary(wineQualityReds$density)

qplot(data = wineQualityReds, x = pH)
summary(wineQualityReds$pH)

qplot(data = wineQualityReds, x = sulphates)
summary(wineQualityReds$sulphates)

qplot(data = wineQualityReds, x = alcohol)
summary(wineQualityReds$alcohol)
```

As a result, 

* Fixed acidity is skewed to the right, with most wines of lesser fixed acidity
from 6 to 8g / dm^3.   
* Volatile acidity is slightly skewed to the right, with most wines of lesser 
volatile acidity from 0.2 to 0.8g / dm^3.   
* Citric acid is used less frequently than other kinds of acid according to 
Wikipedia, so I leave many 0 values in citric acid category as they are.   
* Residual sugar is skewed to the right, with most wines of lesser residual 
sugar from 2 to 4g / dm^3.   
* Chrorides is skewed to the right, with most wines of lesser chlorides from 
0.0 to 0.1g / dm^3.   
* Free sulfur dioxide is skewed to the right, with most wines of lesser free 
surfur dioxide from 0 to 20mg / dm^3.   
* Total sulfur dioxide is skewed to the right, with most wines of lesser total 
surfur dioxide from 0 to 50mg / dm^3.   
* Distribution of density is close to standard diviation, with majority wines 
of 3.3pH.   
* Distribution of pH is close to standard diviation, with majority wines of 
0.997g / dm^3.   
* Alcohol is skewed to the right, with most wines of lesser alcohole from 9 to
10%.   


```{r}
# create a new dataset by removing data whose citric.acid is 0
citricAcidNotZero <- subset(wineQualityReds, citric.acid != 0)

qplot(data = citricAcidNotZero, x = citric.acid, binwidth = 0.01)
summary(citricAcidNotZero$citric.acid)
```

I omitted 0 values from citric.acid category and plotted again. There seems to 
be three peaks at 0.02, 0.24 and 0.49.


For skewed with long features data, I conducted log transformation to better 
understand their distribution and data is showed  as below.

```{r}
plot1 <- qplot(data = wineQualityReds, x = residual.sugar, 
               binwidth = 0.1, fill = I('#099DD9')) + 
  ggtitle('residual.sugar')

plot2 <- qplot(data = wineQualityReds, x = residual.sugar, 
               binwidth = 0.01, fill = I('#F79420')) +
  ggtitle('residual.sugar (log10)') + 
  scale_x_log10()

grid.arrange(plot1, plot2, ncol = 2)

cat("wineQualityReds$residual.sugar")
summary(wineQualityReds$residual.sugar)
cat("log10(wineQualityReds$residual.sugar)")
summary(log10(wineQualityReds$residual.sugar))

plot1 <- qplot(data = wineQualityReds, x = chlorides, 
               binwidth = 0.01, fill = I('#099DD9')) + 
  ggtitle('chlorides')

plot2 <- qplot(data = wineQualityReds, x = chlorides, 
               binwidth = 0.01, fill = I('#F79420')) +
  ggtitle('chlorides (log10)') + 
  scale_x_log10()

grid.arrange(plot1, plot2, ncol = 2)

cat("wineQualityReds$chlorides")
summary(wineQualityReds$chlorides)
cat("log10(wineQualityReds$chlorides)")
summary(log10(wineQualityReds$chlorides))

plot1 <- qplot(data = wineQualityReds, x = total.sulfur.dioxide, 
               binwidth = 0.1, fill = I('#099DD9')) + 
  ggtitle('total.sulfur.dioxide')

plot2 <- qplot(data = wineQualityReds, x = total.sulfur.dioxide, 
               binwidth = 0.01, fill = I('#F79420')) +
  ggtitle('total.sulfur.dioxide (log10)') + 
  scale_x_log10()

grid.arrange(plot1, plot2, ncol = 2)

cat("wineQualityReds$total.sulfur.dioxide")
summary(wineQualityReds$total.sulfur.dioxide)
cat("log10(wineQualityReds$total.sulfur.dioxide)")
summary(log10(wineQualityReds$total.sulfur.dioxide))

plot1 <- qplot(data = wineQualityReds, x = alcohol, 
               binwidth = 0.1, fill = I('#099DD9')) + 
  ggtitle('alcohol')
plot2 <- qplot(data = wineQualityReds, x = alcohol, 
               binwidth = 0.01, fill = I('#F79420')) +
  ggtitle('alcohol (log10)') + 
  scale_x_log10()

grid.arrange(plot1, plot2, ncol = 2)

cat("wineQualityReds$alcohol")
summary(wineQualityReds$alcohol)
cat("log10(wineQualityReds$alcohol)")
summary(log10(wineQualityReds$alcohol))
```

After log transformation,  

* Distibution of residual.sugar is peaking around 3g / dm^3.  
* Distibution of chlorides is peaking around 0.9g / dm^3.  
* Distibution of total.sulfur.dioxide is peaking around 50g / dm^3.  
* Distibution of alcohol is peaking around 8g / dm^3.  

```{r}
# create a new variable "total.acidity" by adding volatile.acidity to fixed.acidity 
wineQualityReds$total.acidity <- wineQualityReds$fixed.acidity + 
  wineQualityReds$volatile.acidity

qplot(data = wineQualityReds, x = total.acidity)
```

Total acidity is slightly skewed to right, with most wines of lesser acidity 
around 7.5g / dm^3. 


I also created 3 categories divided by quality score:

* low: quality score 0 - 4
* middle: quality score 5 - 6
* high: quality score 7 - 10

This would help us to achieve a better understandings rough flow of "quality" feature.

```{r}
# create new variable "quality.cut" with cut function
wineQualityReds$quality.cut <- cut(wineQualityReds$quality, 
                                   breaks=c(-1,4,6,11), 
                                   labels=c("low","middle","high"))

citricAcidNotZero$quality.cut <- cut(citricAcidNotZero$quality, 
                                     breaks=c(-1,4,6,11), 
                                     labels=c("low","middle","high"))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
ordered(wineQualityReds$quality.cut, levels = c("high", "middle", "low"))
```

When I plot quality.cut, it looks like a chart below. 

```{r}
qplot(data = wineQualityReds, x = quality.cut)

summary(wineQualityReds$quality.cut)
```

With this categorization, most of the red wines(1319 out of 1599) fall into 
"middle" section.


# Univariate Analysis
  
  
### What is the structure of your dataset?

There are 1599 red wines in the dataset with 13 attributes (X, fixed.acidity, 
volatile.acidity, citric.acid, residual.sugar, chlorides, free.sulfur.dioxide, 
total.sulfur.dioxide, density, pH, sulphates, alcohol, quality). Quality is 
ordered factorwith integer numbers from 3 to 8. 

Other observations:   

* Mostly red wine quality is 5 or 6.   
* Fixed acidity is skewed to the right, with most wines of lesser fixed acidity 
from 6 to 8g / dm^3.   
* Volatile acidity is slightly skewed to the right, with most wines of lesser 
volatile acidity from 0.2 to 0.8g / dm^3.   
* Citric acid has three peaks at 0.02, 0.24 and 0.49 without 0 values.   
* Residual sugar is skewed to the right, with most wines of lesser residual 
sugar from 2 to 4g / dm^3.   
* Chrorides is skewed to the right, with most wines of lesser chlorides from 
0.0 to 0.1g / dm^3.   
* Free sulfur dioxide is skewed to the right, with most wines of lesser free 
surfur dioxide from 0 to 20mg / dm^3.   
* Total sulfur dioxide is skewed to the right, with most wines of lesser total 
surfur dioxide from 0 to 50mg / dm^3.   
* Distribution of density is close to standard diviation, with majority wines 
of 3.3pH.   
* Distribution of pH is close to standard diviation, with majority wines of 
0.997g / dm^3.   
* Alcohol is skewed to the right, with most wines of lesser alcohole from 9 to 
10%.   

### What is/are the main feature(s) of interest in your dataset?

The main feature of this dataset is quality of red wines and its relation to 
other attributes. I would like to clarify what are the main factors to determine 
wine quality. I hope to create predictive model to wine quality combining some 
variables within the dataset.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

Other features of fixed.acidity, volatile.acidity, citric.acid, residual.sugar, 
chlorides, free.sulfur.dioxide, total.sulfur.dioxide, density, pH, sulphates, 
and alcohol are likely to affect wine quality. After reading some article online,
I suspect volatile acidity and sulphates adversely affect to lower wine quality.

### Did you create any new variables from existing variables in the dataset?

I created a new variable, 'total acidity', by adding fixed acidity and volatile 
acidity to citic acid, because total acidity is one of the important factor to 
evaluate wine quality in balance with sweetness and bitterness. Contrary to pH, 
which refers to strength of acidity, total acidity is total amount of all acids 
present.  

I also created "quality.cut" categorization, which divide wine quality into 
three groups: "low", "middle", "high". There are 63, 1319 and 27 wines in each 
category. I hope this categorization helps us to understand rough tendency of 
good wine / poor wine.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

I log-transformed right skewed distributions, which is residual.sugar, chlorides,
total.sulfur.dioxide and alcohol.

Ovserbations after log-tranformation:   

* Distibution of residual.sugar is peaking around 3g / dm^3.   
* Distibution of chlorides is peaking around 0.9g / dm^3.   
* Distibution of total.sulfur.dioxide is peaking around 50g / dm^3.   
* Distibution of alcohol is peaking around 8g / dm^3.   

# Bivariate Plots Section

  

```{r echo=FALSE}
# remove non-numeric attributes
wineQualityRedsCor <- wineQualityReds[,c(-1,-14,-16)]
wineQualityRedsCor$quality <- as.numeric(wineQualityRedsCor$quality)
cor(wineQualityRedsCor)
```

From the table above, I expect to see correlations between these features;

* residual.sugar and density
* free.sulfur.dioxide and total.sulfur.dioxide
* pH and total.acidity
* pH and citric.acid

Relations of these features and R^2 values are drawn and calculated as below.

```{r}
ggplot(aes(x = residual.sugar, y = density), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of residual.sugar and density")
cat("R^2 value of residual.sugar and density")
summary(lm(residual.sugar ~ density, data=wineQualityReds))$r.squared 

ggplot(aes(x = free.sulfur.dioxide, y = total.sulfur.dioxide), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of free.sulfur.dioxide and total.sulfur.dioxide")
cat("R^2 value of free.sulfur.dioxide and total.sulfur.dioxide")
summary(lm(free.sulfur.dioxide ~ total.sulfur.dioxide, 
           data=wineQualityReds))$r.squared 

ggplot(aes(x = total.acidity, y = pH), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of total.acidity and pH")
cat("R^2 value of total.acidity and pH")
summary(lm(total.acidity ~ pH, data=wineQualityReds))$r.squared 

ggplot(aes(x = citric.acid, y = pH), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of citric.acid and pH")
cat("R^2 value of citric.acid and pH")
summary(lm(citric.acid ~ pH, data=wineQualityReds))$r.squared 

```

Observations:

* "Free.sulfur.dioxide and total.sulfur.dioxide" and "pH and total.acidity" have
strong correlation with about 45% R^2 value.
* pH and citric.acid has moderate correlation with R^2 value 29%.
* Residual.sugar and density has weak correlation with R^2 value 13%.


Also from the correlation table above, "fixed.acidity", "volatile.acidity", 
"citric.acid", "chlorides", "total.sulfur.dioxide", "density", "sulphates", 
"alcohol", and "total.acidity" have higher correlation with quality, so I am 
going to draw a Matrix chart with these features.

```{r echo=FALSE, Bivariate_Plots}
dataForMatrix <- wineQualityReds[2:4,6:7,9:14]
columnList <- 
  c("fixed.acidity", "volatile.acidity", "citric.acid", "chlorides", 
    "total.sulfur.dioxide", "density", "sulphates", "alcohol", "quality", 
    "total.acidity" )
dataForMatrix <- wineQualityReds[, columnList]

chart.Correlation(dataForMatrix, histogram=TRUE, pch=19)
```

**Quality**  

* All features do not seem to have strong correlations, but moderately 
correlated with quality.

**fixed.acidity**

* has strong positive correlation with citric.acid and density.

**volatile.acidity**

* has strong negative correlation with citric.acid.

**citric.acid**

* has moderate positive correlation with chlorides, density and sulphates.

**chlorides**

* has moderate positive correlation with density and sulphates.
* has moderate negative correlation with alcohol.

**total.sulfur.dioxide**

* has moderate negative correlation with alcohol.

**density**

* has strong negative correlation with alcohol.
* has moderate positive correlation with sulphates.  
  
  
About these correlations, I want to look closer at scatter plots and box plots.  
   
  
**Quality**
  
  
```{r}
# box plot of fixed.acidity
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = fixed.acidity)) + 
  geom_boxplot() + 
  ggtitle("quality and fixed.acidity data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = fixed.acidity)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and fixed.acidity data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)

# box plot of volatile.acidity
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = volatile.acidity)) + 
  geom_boxplot() + 
  ggtitle("quality and volatile.acidity data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = volatile.acidity)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and volatile.acidity data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)

# box plot of citric.acid
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = citric.acid)) + 
  geom_boxplot() + 
  ggtitle("quality and citric.acid data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = citric.acid)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and citric.acid data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)

# box plot of chlorides
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = chlorides)) + 
  geom_boxplot() + 
  ggtitle("quality and chlorides data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = chlorides)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and chlorides data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)

# box plot of total.sulfur.dioxide
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = total.sulfur.dioxide)) + 
  geom_boxplot() + 
  ggtitle("quality and total.sulfur.dioxide data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = total.sulfur.dioxide)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and total.sulfur.dioxide data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)

# box plot of density
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = density)) + 
  geom_boxplot() + 
  ggtitle("quality and density data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = density)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and density data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)

# box plot of sulphates
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = sulphates)) + 
  geom_boxplot() + 
  ggtitle("quality and sulphates data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = sulphates)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and sulphates data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)

# box plot of alcohol
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = alcohol)) + 
  geom_boxplot() + 
  ggtitle("quality and alcohol data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = alcohol)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and alcohol data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)

# box plot of total.acidity
plot1 <- ggplot(wineQualityReds, aes(x = quality.factor, y = total.acidity)) + 
  geom_boxplot() + 
  ggtitle("quality and total.acidity data") + 
  labs(x = "quality")

plot2 <- ggplot(wineQualityReds, aes(x = quality.cut, y = total.acidity)) + 
  geom_boxplot() + 
  ggtitle("quality.cut and total.acidity data") + 
  labs(x = "quality.cut")

grid.arrange(plot1, plot2, ncol = 2)
```


Findings from box plots:  

* Amount of fixed acidity is almost the same for all quality of wines, except 
slightly hier for wines with score 7.
* The more volatile acidity a wine has, the lower quality it scores.
* The more citric acid a wine has, the higher quality it scores.
* Median of chlorides do not differ much between qulaities, but wines with 
quality score 5 and 6 have more outliers abpve upper quartile.
* Correlation of total sulfur dioxide and quality is positive for wines with 
quality score  from 3 to 5, however it turns to negatove for wines whose quality
score is between 5 to 8.
* Density is mostly negatively correlated to quality, especially for wines with 
score 7 and 8. 
* Sulphates has positive correlation with quality.
* Alcohol is positively correlated to quality, especially for wines with score 
above 6.

I calculated statistical scores of variables which might have correlation with 
quality.

Quality and volatile.acidity
```{r}
exponential.model <- 
  lm(quality~volatile.acidity, 
     data = subset(wineQualityReds, 
                   volatile.acidity <= 
                     quantile(wineQualityReds$volatile.acidity, 0.999)))

summary(exponential.model)
```

Quality and citric.acid
```{r}
exponential.model <- 
  lm(quality~citric.acid, 
     data = subset(wineQualityReds, 
                   citric.acid <= quantile(wineQualityReds$citric.acid, 0.999)))

summary(exponential.model)
```


Quality and alcohol
```{r}
exponential.model <- 
  lm(quality~alcohol, 
     data = subset(wineQualityReds, 
                   alcohol <= quantile(wineQualityReds$alcohol, 0.999)))

summary(exponential.model)
```

  
From the result of R^2 scores,   

* Volatile.acidity explains about 15% of the variance in quality.
* Citric acid explains about only 5% of the variance in quality.
* Alcohol explains about 23% of the variance in quality.


```{r}
# create new datasets by subsetting with quality score
wineQualityReds3 <- subset(wineQualityReds, quality == 3)
wineQualityReds4 <- subset(wineQualityReds, quality == 4)
wineQualityReds5 <- subset(wineQualityReds, quality == 5)
wineQualityReds6 <- subset(wineQualityReds, quality == 6)
wineQualityReds7 <- subset(wineQualityReds, quality == 7)
wineQualityReds8 <- subset(wineQualityReds, quality == 8)

cat("wine quality: 3")
summary(wineQualityReds3$citric.acid)
cat("wine quality: 4")
summary(wineQualityReds4$citric.acid)
cat("wine quality: 5")
summary(wineQualityReds5$citric.acid)
cat("wine quality: 6")
summary(wineQualityReds6$citric.acid)
cat("wine quality: 7")
summary(wineQualityReds7$citric.acid)
cat("wine quality: 8")
summary(wineQualityReds8$citric.acid)
```

Although I suspected that citric.acid is one of the cause of wine fault, against
my intuition minimum number is largest at quality 8.

While 2 < quality < 6:

```{r}
# dataset with quality 3 or 4 or 5
wineQualityReds35 <- subset(wineQualityReds, 
                            quality == 3 | quality == 4 | quality == 5)

exponential.model1 <- 
  lm(quality~total.sulfur.dioxide, 
     data = subset(wineQualityReds35, 
                   total.sulfur.dioxide <= 
                     quantile(wineQualityReds35$total.sulfur.dioxide, 0.999)))

summary(exponential.model1)
```

While 5 < quality < 9:

```{r}
# dataset with quality 6 or 7 or 8
wineQualityReds68 <- subset(wineQualityReds, 
                            quality == 6 | quality == 7 | quality == 8)

exponential.model2 <- 
  lm(quality~total.sulfur.dioxide, 
     data = subset(wineQualityReds68, 
                   total.sulfur.dioxide <= 
                     quantile(wineQualityReds68$total.sulfur.dioxide, 0.999)))

summary(exponential.model2)
```
  
When I split the dataset into two groups: one is wine quality of 3-5, another is
wine quality of 6-8, total.sulfur.dioxide explains only about 3% for wine of 
quality score 3-5 and 1% for wine of quality score 6-8.
  
  
  
**fixed.acidity**

From the chart matrix, fixed.acidity seems to have strong positive correlation 
with citric.acid and density.

```{r}
ggplot(aes(x = citric.acid, y = fixed.acidity), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of citric.acid and fixed.acidity")

exponential.model <- 
  lm(fixed.acidity~citric.acid, 
     data = subset(wineQualityReds, 
                   citric.acid <= quantile(wineQualityReds$citric.acid, 0.999)))

summary(exponential.model)
```

From the R^2 = 0.45, the variance in fixed.acidity is explainted with 
citric.acid by about 45%.
  
    
**volatile.acidity**

From the chart matrix, volatile.acidity seems to have strong negative 
correlation with citric.acid.

```{r}
ggplot(aes(x = citric.acid, y = volatile.acidity), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of citric.acid and volatile.acidity")

exponential.model <- 
  lm(volatile.acidity~citric.acid, 
     data = subset(wineQualityReds, 
                   citric.acid <= quantile(wineQualityReds$citric.acid, 0.999)))

summary(exponential.model)
```

Based on the R^2 value, citric.acid explains about 31% of the variance in 
volatile.acidity.
  
   
**citric.acid**

From the chart matrix, citric.acid seems to have moderate positive correlation 
with chlorides, density and sulphates.

```{r}
ggplot(aes(x = chlorides, y = citric.acid), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of chlorides and citric.acid")

exponential.model <- 
  lm(chlorides~citric.acid, 
     data = subset(wineQualityReds, 
                   chlorides <= quantile(wineQualityReds$chlorides, 0.999)))

summary(exponential.model)
```

```{r}
ggplot(aes(x = density, y = citric.acid), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of density and citric.acid")

exponential.model <- 
  lm(density~citric.acid, 
     data = subset(wineQualityReds, 
                   density <= quantile(wineQualityReds$density, 0.999)))

summary(exponential.model)
```

```{r}
ggplot(aes(x = sulphates, y = citric.acid), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of sulphates and citric.acid")

exponential.model <- 
  lm(sulphates~citric.acid, 
     data = subset(wineQualityReds, 
                   sulphates <= quantile(wineQualityReds$sulphates, 0.999)))

summary(exponential.model)
```

Based on the R^2 value, chlorides and sulphates explains about less than 10% of
the variance in citric.acid, on the other hand, density does about 13%.
  
  
**chlorides**

From the chart matrix, chlorides seems to have moderate positive correlation 
with density and sulphates and negative correlation with alcohol.

```{r}
ggplot(aes(x = density, y = chlorides), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of density and chlorides")


exponential.model <- 
  lm(chlorides~density, 
     data = subset(wineQualityReds, 
                   density <= quantile(wineQualityReds$density, 0.999)))

summary(exponential.model)
```


```{r}
ggplot(aes(x = sulphates, y = chlorides), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of sulphates and chlorides")

exponential.model <- 
  lm(chlorides~sulphates, 
     data = subset(wineQualityReds, 
                   sulphates <= quantile(wineQualityReds$sulphates, 0.999)))

summary(exponential.model)
```

```{r}
ggplot(aes(x = alcohol, y = chlorides), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of alcohol and chlorides")

exponential.model <- 
  lm(chlorides~alcohol, 
     data = subset(wineQualityReds, 
                   alcohol <= quantile(wineQualityReds$alcohol, 0.999)))

summary(exponential.model)
```


Based on the R^2 value, density and alcohol explains about less than 10% of the 
variance in chlorides, on the other hand, sulphates does about 12%.
  
  
**total.sulfur.dioxide**

From the chart matrix, total.sulfur.dioxide seems to have moderate negative 
correlation with alcohol.


```{r}
ggplot(aes(x = alcohol, y = total.sulfur.dioxide), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of alcohol and total.sulfur.dioxide")

exponential.model <- 
  lm(total.sulfur.dioxide~alcohol, 
     data = subset(wineQualityReds, 
                   alcohol <= quantile(wineQualityReds$alcohol, 0.999)))

summary(exponential.model)
```

Based on the R^2 value, alcohol explains only about 4% of the variance in 
total.sulfur.dioxide.
  
  
**density**

From the chart matrix, density seems to have strong negative correlation with 
alcohol and moderate positive correlation with sulphates. 

```{r}
ggplot(aes(x = alcohol, y = density), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of alcohol and density")

exponential.model <- 
  lm(density~alcohol, 
     data = subset(wineQualityReds, 
                   alcohol <= quantile(wineQualityReds$alcohol, 0.999)))

summary(exponential.model)
```

```{r}
ggplot(aes(x = sulphates, y = density), data = wineQualityReds) + 
  geom_point(alpha = 0.5) + 
  ggtitle("Plot of sulphates and density")

exponential.model <- 
  lm(density~sulphates, 
     data = subset(wineQualityReds, 
                   sulphates <= quantile(wineQualityReds$sulphates, 0.999)))

summary(exponential.model)
```

Based on the R^2 value, alcohol explains about 25% of the variance in density, 
but sulphates does only about 2%.

To sum up this section, although volatile.acidity, citric.acid, 
total.sulfur.dioxide and alcohol seemed to have correlation with quality from 
boxplots, their R^2 value was not high. There might be too many outliers or 
other factors to affect quality. Also, minimum citric.acid was biggest within 
the data subset of quality score 8. This was against my expectation that 
citric.acid adds unpleasant taste to wine. Again, based on the R^2 value, 
correlation between alcohol and density was unexpectedly high at 25%.
  
# Bivariate Analysis

  

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features \
in the dataset?

From observation of box plots which include quality and other features' data:  

* Amount of fixed acidity is almost the same for all quality of wines, except 
slightly hier for wines with score 7.
* The more volatile acidity a wine has, the lower quality it scores.
* The more citric acid a wine has, the higher quality it scores.
* Median of chlorides do not differ much between qulaities, but wines with 
quality score 5 and 6 have more outliers above upper quartile.
* Correlation of total sulfur dioxide and quality is positive for wines with 
quality score  from 3 to 5, however it turns to negatove for wines whose quality
score is between 5 to 8.
* Density is mostly negatively correlated to quality, especially for wines with 
score 7 and 8. 
* Sulphates has positive correlation with quality.
* Alcohol is positively correlated to quality, especially for wines with score 
above 6.
  
From observation of matrix chart of some attributes(fixed.acidity, 
volatile.acidity, citric.acid, chlorides, total.sulfur.dioxide, density, 
sulphates, alcohol, and total.acidity:  

* Fixed.acidity has strong positive correlation with citric.acid and density.
* Volatile.acidity has strong negative correlation with citric.acid.
* Citric.acid has moderate positive correlation with chlorides, density and 
sulphates.
* Chlorides has moderate positive correlation with density and sulphates and 
moderate negative correlation with alcohol.
* Total.sulfur.dioxide has moderate negative correlation with alcohol.
* Density has strong negative correlation with alcohol.
* Density has moderate positive correlation with sulphates. 

From observation of a correlation table which include all features:

* "Free.sulfur.dioxide and total.sulfur.dioxide"" and "pH and total.acidity" 
have strong correlation with about 45% R^2 value.
* pH and citric.acid has moderate correlation with R^2 value 29%.
* Residual.sugar and density has weak correlation with R^2 value 13%.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

With R^2 value basis, correlation between alcohol and density is unexpectedly 
high at about 25%. After I searched online to know that alcohol density is 
0.8g/ml, this looks more natural now though.

### What was the strongest relationship you found?

Based on R^2 value to explain the variance in quality, alcohol explains about 
23% and the most. Although its R^2 score is not as high as alcohol, 
volatile.acidity also explains variance in wine quality by anout 15%.
    
   
# Multivariate Plots Section

From the bivariate plots, I expect to find more relations with wine quality and 
other attributions; volatile.acidity, citric.acid, total.sulfur.dioxide, 
density, sulphates, and alcohol. Also, since alcohol seems to be one of the 
important factor for good wine, I would like to explore more about relations 
between alcohol and seemingly correlated attributions; chlorides, 
total.sulfur.dioxide and density. 

**Alcohol and chlorides, total.sulfur.dioxide and density**

I created scatter plots of conbinations of chlorides and density, 
total.sulfur.dioxide and density, total.sulfur.dioxide and chlorides, 
conducting log-tranformation for skewed distribution data.   

```{r}
# draw scatter plot with log10(chlorides) and density, coloring by alcohol
ggplot(aes(x = log10(chlorides), y = density, color = alcohol), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5, aes(color = alcohol)) +
  scale_colour_gradient(low = wes_palette("Zissou1")[1], 
                        high = wes_palette("Zissou1")[4]) + 
  ggtitle("Plot of log10(chlorides) and density colored by alcohol")
```

```{r}
# draw scatter plot with log10(total.sulfur.dioxide) and density, coloring by alcohol
ggplot(aes(x = log10(total.sulfur.dioxide), y = density, color = alcohol), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5, aes(color = alcohol)) +
  scale_colour_gradient(low = wes_palette("Zissou1")[1], 
                        high = wes_palette("Zissou1")[4]) + 
  ggtitle("Plot of log10(total.sulfur.dioxide) and density colored by alcohol")
```

```{r}
# draw scatter plot with log10(total.sulfur.dioxide) and log10(chlorides), coloring by alcohol
ggplot(aes(x = log10(total.sulfur.dioxide), 
           y = log10(chlorides), color = alcohol), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5, aes(color = alcohol)) +
  scale_colour_gradient(low = wes_palette("Zissou1")[1], 
                        high = wes_palette("Zissou1")[4]) + 
  ggtitle("Plot of log10(total.sulfur.dioxide) and log10(chlorides) 
          colored by alcohol")
```

From the plots, chlorides and density combination seems to have the strongest 
correlation with alcohol among three. I wonder how it looks like when it is 
divided by quality and removed outliers.

```{r}
# draw scatter plot with log10(chlorides) and density, coloring by alcohol
ggplot(aes(x = log10(chlorides), y = density, color = alcohol), 
       data = subset(wineQualityReds, 
                     density <= quantile(wineQualityReds$density, 0.999))) + 
  geom_point(alpha = 0.5, aes(color = alcohol)) +
  scale_colour_gradient(low = wes_palette("Zissou1")[1], 
                        high = wes_palette("Zissou1")[4]) + 
  ggtitle("Plot of log10(chlorides) and density colored by alcohol") +
  facet_grid(cols = vars(quality))
```

By removing a part of density data, which is above third quartile, and dividing 
by quality, it became clearer that as the higher density a wine has, the lower 
percentage of alcohol it contains. Also, a wine with density below 0.9925 is 
likely to fall into quality score 6 and wine with density above 1.0000 is likely
to have quality score 5 or 6.


**Quality and volatile.acidity, citric.acid, total.sulfur.dioxide, density, \
sulphates, and alcohol**

Ovserbing the bivariate plots, I suspected there are different trends between 
wines of low quality and middle quality and high quality. So I have plotted '
volatile.acidity, citric.acid, total.sulfur.dioxide, density, sulphates, and 
alcohol combinations colored by quality.cut. From the univariate and bivariate 
analysis, I expected that citric.acid, sulphates and alcohol have relatively 
positive correlation and that volatile.acidity and density have relatively 
negative correlation with quality. Also, total.sulfur.dioxide's distribution 
seems to be close to standard diviation over quality. Combining positive and 
negative correlated features each other, I plotted three scatter plots: "alcohol 
and citric.acid", "sulphates and citric.acid", "total.sulfur.dioxide and 
citric.acid", "volatile.acidity and density" and "volatile.acidity and 
total.sulfur.dioxide" colored by quality.cut. For skewed data, log 
transformation is applied, so that their tendency of distribution becomes 
clearer. When plotting citric.acid, data with citric.acid == 0 is removed, 
for easier observation of correlation.


```{r}
# draw scatter plot with log10(citric.acid) and alcohol, coloring by quality.cut
ggplot(aes(x = alcohol, y = log10(citric.acid), color = quality.cut), 
       data = citricAcidNotZero) + 
  geom_point(alpha = 0.5) +
  #facet_grid(cols = vars(quality.cut)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut") +
  theme(aspect.ratio = 1) + 
  ggtitle("Plot of alcohol and log10(citric.acid) colored by quality.cut")

# draw scatter plot with log10(sulphates) and citric.acid, coloring by quality.cut
ggplot(aes(x = log10(sulphates), y = citric.acid, color = quality.cut), 
       data = citricAcidNotZero) + 
  geom_point(alpha = 0.5) +
  #facet_grid(cols = vars(quality.cut)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut") +
  theme(aspect.ratio = 1) + 
  ggtitle("Plot of log10(sulphates) and citric.acid colored by quality.cut")

# draw scatter plot with log10(total.sulfur.dioxide and citric.acid, coloring by quality.cut
ggplot(aes(x = log10(total.sulfur.dioxide), 
           y = citric.acid, color = quality.cut), 
       data = citricAcidNotZero) + 
  geom_point(alpha = 0.5) +
  #facet_grid(cols = vars(quality.cut)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut") +
  theme(aspect.ratio = 1) + 
  ggtitle("Plot of log10(total.sulfur.dioxide) and citric.acid colored by 
          quality.cut")

# draw scatter plot with log10(volatile.acidity) and density, coloring by quality.cut
ggplot(aes(x = log10(volatile.acidity), y = density, color = quality.cut), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5) +
  #facet_grid(cols = vars(quality.cut)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut") +
  theme(aspect.ratio = 1) + 
  ggtitle("Plot of log10(volatile.acidity) and density colored by quality.cut")

# draw scatter plot with log10(volatile.acidity) and log10(total.sulfur.dioxide), coloring by quality.cut
ggplot(aes(x = log10(volatile.acidity), 
           y = log10(total.sulfur.dioxide), 
           color = quality.cut), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5) +
  #facet_grid(cols = vars(quality.cut)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut") +
  theme(aspect.ratio = 1) + 
  ggtitle("Plot of log10(volatile.acidity) and log10(total.sulfur.dioxide) 
          colored by quality.cut")

```

Among three plots above, the plot of log10(sulphates) and citric.acid is showing
the clearest correlation with quality and each attributions. Good wine tends to 
have more citric.acid and sulphates, apperaing on the upper right.
  
    
Since R^2 score in correlation with quality was highest for alcohol(25%) and 
volatile.acidity(15%), I have plotted a scatter plot with these two features, 
too.  
  

```{r}
# draw scatter plot with volatile.acidity and alcohol, coloring by quality.cut
ggplot(aes(x = volatile.acidity, y = alcohol, color = quality.cut), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5) +
  #facet_grid(cols = vars(quality.cut)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut") +
  theme(aspect.ratio = 1) + 
  ggtitle("Plot of volatile.acidity and alcohol colored by quality.cut")
```

Thus good wines are mainly grouped on the upper left with higher percentage of 
alcohol and lesser volatile.acidity.   

  
I would like to explore more about correlations between log10(sulphates) and 
citric.acid, and volatile.acidity and alcohol.

```{r}
# create new variable by log-transforming wineQualityReds$sulphates
wineQualityReds$log10.sulphates <- log10(wineQualityReds$sulphates)

lm <- lm(log10.sulphates~citric.acid, wineQualityReds)

# draw scatter plot with log10(sulphates) and citric.acid, coloring by quality.cut
ggplot(aes(x = log10.sulphates, y = citric.acid, color = quality.cut), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5) +
  facet_grid(cols = vars(quality)) + 
  geom_smooth(method='lm') +
  ggtitle("Plot of log10.sulphates and citric.acid") + 
  facet_grid(cols = vars(quality)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut")

mtable(lm)
```

It is interesting that correlation is turning to negative only for wine with 
quality score 8 and variance of log10(sulphates) is smaller.

```{r}
lm <- lm(volatile.acidity~alcohol, wineQualityReds)

# draw scatter plot with volatile.acidity and alcohol, coloring by quality.cut
ggplot(aes(x = volatile.acidity, y = alcohol, color = quality.cut), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5) +
  facet_grid(cols = vars(quality)) + 
  geom_smooth(method='lm') +
  ggtitle("Plot of volatile.acidity and alcohol") + 
  facet_grid(cols = vars(quality)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut")

mtable(lm)
```

There is a strong correlation between alcohol and volatile.acidity for data 
points with quality == 3 or 8.  
  

To summarize, 

* Based on the plot of log10(chlorides) and density, 
    + density and alcohol have correlation.
    + log10(chlorides) and alcohol have weak correlation.
    + density of below 0.9925 data points are good wine scoring 6 to 8.
    + density of above 1.0000 data points are tend to be good wine scoring 5 to 
    7.
* From the plot of log10(sulphates) and citric.acid,
    + good wine tends to appear on the upper right of plots with more 
    citric.acid and sulphates.
    + its correlation is positive for data points with quality score 3 to 7, 
    but turns negative for data points with quality == 8.
* From the plot of volatile.acidity and alcohol,
    + good wine tends to appear on the upper left with higher percentage of 
    alcohol and lesser volatile.acidity.
    + its correlation is more obvious for data with quality score 3 or 8.
   
    

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

Volatile.acidity and alcohol seem to have the best combination to look at wine 
quality. Looking at a plot of volatile.acidity and alcohol, good wines are 
mainly positioned on the upper left with higher percentage of alcohol and lesser 
volatile.acidity. A plot of log10 transformation of sulphates and citric.acid 
also shows correlation each other. Here good wines are on upper right corner 
with bigger number of log10(sulphates) and more citric.acid.

### Were there any interesting or surprising interactions between features?

On the plot of log10(chlorides) and density, by removing a part of density data, 
which is above third quartile, and dividing by quality, it became clearer that 
as the higher density a wine has, the lower percentage of alcohol it contains. 
Also, a wine with density below 0.9925 is likely to fall into quality score 6 or 
7 or 8 and wine with density above 1.0000 is likely to have quality score 5 or 6. 
It is interesting that although there is no strong correlation, lesser density 
wine tends to be a good one.

### OPTIONAL: Did you create any models with your dataset? Discuss the strengths \
and limitations of your model.

------

# Final Plots and Summary

  
   

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(aes(x = log10(chlorides), y = density, color = alcohol), 
       data = subset(wineQualityReds, 
                     density <= quantile(wineQualityReds$density, 0.999))) + 
  geom_point(alpha = 0.5, aes(color = alcohol)) +
  scale_colour_gradient(low = wes_palette("Zissou1")[1], 
                        high = wes_palette("Zissou1")[4]) + 
  ggtitle("Plot of log10(chlorides(g / dm^3)) and density(g / dm^3) colored by 
          alcohol") +
  facet_grid(cols = vars(quality)) + 
  scale_x_unit(unit = 'g / dm^3') +
  scale_y_unit(unit = 'g / dm^3')
```

### Description One
This plot indicates correlation between alcohol and quality. Also, when density 
is below 0.9925 or above 1.000, quality seems to fall above 5.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(aes(x = log10(sulphates), y = citric.acid, color = quality.cut), 
       data = citricAcidNotZero) + 
  geom_point(alpha = 0.5) +
  #facet_grid(cols = vars(quality.cut)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut") +
  theme(aspect.ratio = 1) + 
  ggtitle("Plot of log10(sulphates(g / dm^3)) and citric.acid(g / dm^3) colored 
          by quality.cut") + 
  scale_x_unit(unit = 'g / dm^3') +
  scale_y_unit(unit = 'g / dm^3')
```

### Description Two
From this plot, correlation between quality and citric.acid and log10(sulphates) 
can be seen. 

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x = volatile.acidity, y = alcohol, color = quality.cut), 
       data = wineQualityReds) + 
  geom_point(alpha = 0.5) +
  facet_grid(cols = vars(quality)) + 
  geom_smooth(method='lm') +
  ggtitle("Plot of volatile.acidity(g / dm^3) and alcohol(%)") + 
  facet_grid(cols = vars(quality)) + 
  scale_color_manual(values = wes_palette("GrandBudapest1"), 
                     name = "quality.cut") + 
  scale_x_unit(unit = 'g / dm^3') +
  scale_y_unit(unit = '%')
```

### Description Three
This plot is showing correlation between quality and alcohol and 
volatile.acidity, and at the same time, stronger correlation between alcohol and 
volatule.acidity at score 3 and 8.

------

# Reflection

  
   

This red wine data contains 1599 data with 13 attribution. Not bwing familiar 
with wine tasting, I had to start from understanding what each attribute means 
and how they affect to wine taste. After all, there seemed to be no paired effect 
of wine taste to each attribute. As the amount of attributes varies, wine quality 
also varies non-linearly. That is why I used matrix chart to find relatively 
correlated attributes to quality. From this chart, I cound find alcohol, 
sulphates, density, total.sulfur.dioxide, citric.acid and volatile.acidity had 
relatively strong relation with quality. From online articles I read I was 
minunderstanding that citric.acid gives fault to wine taste, so I was feeling 
dtrange when I found positive correlation between quality and citric.acid. 
I searched again then correctly understood that citric.acid gives wine teste 
flaw only after they are consumed too much.
For a future work, wine taste seems to be compounded with several features and 
balances of each features, it would be possible to investigate further for 
appropriate compositionand balance to predict a good wine. 

# Citation

[1] Kaggle. Red Wine Dataset. Retrieved from 
https://www.kaggle.com/piyushgoyal443/red-wine-dataset#wineQualityInfo.txt  
[2] P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. Modeling wine 
preferences by data mining from physicochemical properties. In Decision Support 
Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236. Available at: [@Elsevier] 
http://dx.doi.org/10.1016/j.dss.2009.05.016  
[3] ScienceDirect. Wine Quality. Retrieved from 
https://www.sciencedirect.com/topics/food-science/wine-quality  
[4] Wikipedia. acids in wine. https://en.wikipedia.org/wiki/Acids_in_wine  
[5] Wikipedia. wine fault. Retrieved from 
https://en.wikipedia.org/wiki/Wine_fault#Acetic_acid  
[6] Wine in Moderation.com. How many grams of alcohol in wine?. Retrieved from https://www.wineinmoderation.eu/en/articles/How-many-grams-of-alcohol-in-wine.154/  



  